### 2022-10-26 manuscript.tex
Update cover-letter-submission.Rmd [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332319562

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/d9023c5954b959cbeee18d64728f6cc4f4caff03/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/d9023c5954b959cbeee18d64728f6cc4f4caff03}{SORTEE-Github-Hackathon/manuscript@d9023c5}
on October 26, 2022.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/82d8f8423ae39d95f7eb1d44a90ac5b2055f6267}{SORTEE-Github-Hackathon/manuscript@82d8f84}
on October 26, 2022.
